---
title: "regression"
author: "Akira MATSUI"
date: 
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Using Regression to a report


When you want to use R as a data analysis tool, you must be writing a paper for some propose (for example, a term paper, report ..etc). In this exercise, you firstly conduct a simple regression analysis by using the built in iris data set . Next, you will wrap up an analyzed data and write a paper on `LaTex` format by using `stargaizer`.

# Questions

- Regress Sepal.Length with Sepal.Width, Petal.Length and Petal.Width
- Use stargaizer your result to a latex format 
- convert latex to pdf


# Sample Answer

## Iris Data

`R` already has Iris data set. You can check it by

```{r eval=TRUE, echo=TRUE, error=FALSE}
head(iris)
```
.

If you want to see `Sepal.Length` of iris data, you can access it by

```{r, echo=TRUE, error=FALSE}
head(iris["Sepal.Length"])
```

## Regression

R provide regression function `lm()`

```
lm(dependent variable ~ independent variable0 + independent variable1 + ... , data="Data Frame" )
```

In this case, `Data Frame` is `iris`. The regression analysis we are supposed to conduct is 

```{r, error=FALSE, results=TRUE}
result <- lm (Sepal.Length ~ Sepal.Width + Petal.Length + Petal.Width , data=iris)
summary(result)
```
.

## Stargayzer

`Stargayzer` makes your result attractive. If you do not have `stargayzer` library, you can get and load it via

```{r eval=FALSE, error=FALSE}
install.packages('stargayzer')
library(stargazer)
```
.

It convert `result` to latex format.

```{r eval=FALSE ,error=FALSE}
stargazer(result)
```


It also provides a text format


```{r eval=FALSE, error=FALSE}
stargazer(result, type="text")
```
```
===============================================
                        Dependent variable:    
                    ---------------------------
                           Sepal.Length        
-----------------------------------------------
Sepal.Width                  0.651***          
                              (0.067)          
                                               
Petal.Length                 0.709***          
                              (0.057)          
                                               
Petal.Width                  -0.556***         
                              (0.128)          
                                               
Constant                     1.856***          
                              (0.251)          
                                               
-----------------------------------------------
Observations                    150            
R2                             0.859           
Adjusted R2                    0.856           
Residual Std. Error      0.315 (df = 146)      
F Statistic          295.539*** (df = 3; 146)  
===============================================
Note:               *p<0.1; **p<0.05; ***p<0.01
```